Implementing \Kwd{DNS} in \Kwd{C0}

### 2017-12-11 paper.tex
fix typo

Contrary to \Kwd{Nail}, our approach was to code parsers and
formatters for the \Kwd{DNS} data structures \emph{manually}, but in
memory-safe and type-safe language. This means that while functional
correctness is not guaranteed, \emph{safety} is guaranteed.

>>>>

Contrary to \Kwd{Nail}, our approach was to code parsers and
formatters for the \Kwd{DNS} data structures \emph{manually}, but in a
memory-safe and type-safe language. This means that while functional
correctness is not guaranteed, \emph{safety} is guaranteed.
